---
title: 'Getting Started'
output: html_notebook
---

# Adverse Events

## Accessing Data

```{r setup}
library(ggthemes)
library(readr)
library(GGally)
library(gridExtra)
library(kableExtra)
library(tidyverse)
library(GGally)
```


Next, we'll write some helper functions to use the openFDA API and package to query adverse events data.

```{r mtp}
# Load Data

MTP_Data <- read_csv("MTP_Data.csv")
mtp_data2 <- read_csv("mtp_data2.csv")

mtp <- mtp_data2 %>% left_join(MTP_Data)

#Initial Review of the data
glimpse(mtp)
```

Using our openFDA helper functions, we can pull adverse event data by gender for a specific drug and age range. We can also lookup the drug's active ingredients.

```{r pull-data}
mtp<- mutate(mtp, TotalSale = units*price) %>% mutate(mtp, TotalVolume = units*volume) %>% separate(brand, into = c("company", "brand"), sep = "\\ ", extra = "merge")


mtp$promo<- factor(mtp$promo)
mtp$promo<- recode(mtp$promo, "0" = "No Promo", "1" = "Promo")
mtp$ad<- recode(mtp$ad, "NONE" = "No Ad", "A" = "Big Ad", "B" = "Mid/Small Ad")
mtp$company<- recode(mtp$company, "GENERAL" = "GENERAL MILLS")
mtp$brand<- recode(mtp$brand, "MILLS CINNAMON TST CR" = "CINNAMON TST CR")

mtp$brand<- recode(mtp$brand, "MILLS CHEERIOS" = "CHEERIOS")

mtp$brand<- recode(mtp$brand, "MILLS LUCKY CHARMS" = "LUCKY CHARMS")

mtp$brand<- recode(mtp$brand, "MILLS COCOA PUFFS" = "COCOA PUFFS")

mtp$brand<- recode(mtp$brand, "MILLS KIX" = "KIX")

#review the updated data
glimpse(mtp)

distinct(mtp, brand)




# create_price <- function(min, max){# sprintf('[%f+TO+%f]', min, max)}

company_name <- "KELLOGGS"



# specify age range
# price2 <- create_price(.5,2)


mtp_KELLOGGS <- filter(mtp, company == company_name )

```

## Plotting

Now we're ready to start investigating the data and showing off the resulting graphics. We'll create plots and then a static dashboard.

```{r plots}
mtp_KELLOGGS %>% 
  group_by(brand) %>% 
  summarise(units = sum(units)) %>% 
  ggplot() +
  geom_bar(aes(reorder(brand,units), units), stat = 'identity') +
  coord_flip() +
  labs(
    title = company_name,
    x = NULL,
    y = NULL
  ) +
  theme_minimal()
```

```{r gender}
  # plot by gender
ggplot(mtp_KELLOGGS) +
  geom_bar(aes(reorder(brand,units), units, fill = flavor), stat = 'identity') +
  facet_wrap(~flavor)+
  coord_flip() +
  labs(
    title = company_name,
    x = NULL,
    y = NULL
  ) +
  theme_minimal() + 
  guides(fill = FALSE) + 
  scale_fill_manual(values = c("#d54a30","#4c83b6", "#d0d530", "#9030d5"))

```
