---
title: "Main Document"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(blastula)
library(readr)
```

# An R Markdown Document (Main Report)

This is an **R Markdown** document. *Markdown* is a simple formatting syntax for writing on the web. **R Markdown** takes this a step further by combining *Markdown* prose and **R** code into reproducible documents that can be output as HTML, PDF, Word, and many more output formats. For more details on using **R Markdown**, have a look through [its documentation site](https://rmarkdown.rstudio.com/docs/).

Here is some **R** code, which is contained within a code chunk:

```{r mtp_plot}

mtp <- read_csv("mtp.csv")

mtp %>%
  filter(!(brand %in% c("GENERAL MILLS CINNAMON TST CR", "GENERAL MILLS CHEERIOS", 
                          "GENERAL MILLS LUCKY CHARMS", "GENERAL MILLS COCOA PUFFS", "GENERAL MILLS KIX", "POST SHREDDED WHEAT", 
                          "POST GRAPE NUTS"))) %>%
    filter(package %in% "BOX") %>%
    filter(!(ad %in% "NONE")) %>%
    ggplot() +
    aes(x = units) +
    geom_histogram(bins = 30L, fill = "#0c4c8a") +
    theme_minimal() +
    facet_wrap(vars(brand))
```

Let's get some summarized data about yearly home sales in Dallas, TX and also write that data to a CSV file:

```{r mtp_KELLOGGS}

company_name <- "KELLOGGS"

mtp_KELLOGGS <- filter(mtp, company == company_name ) %>%
  group_by(brand) %>%
  summarize(total_sales = sum(TotalSale, na.rm = TRUE))

mtp_KELLOGGS
```

It looks like the brand `r mtp_KELLOGGS %>% filter(total_sales == max(total_sales)) %>% pull(brand)` had the greatest number of sales. Let's create a CSV for distribution (this code chunk that generates the CSV is ultimately not shown because we used `echo=FALSE` as a chunk option).

```{r write_csv, echo=FALSE}
mtp_KELLOGGS %>% write_csv("mtp_KELLOGGS.csv")
```

We can create an email on **RStudio Connect** that aligns with the content from this report. We do this with the `render_connect_email()` and `attach_connect_email()` functions from the **blastula** package. The email subdocument (`"connect-example-email.Rmd"`) is used to craft the contents of the email, drawing upon results available in this document. Attachments for the email can added by using the arguments:

- `attachments` (for any output files or included files)
- `attach_output` (which attaches the rendered report)

```{r connect_email_setup, echo=FALSE}
render_connect_email(input = "connect-example-email.Rmd") %>%
  attach_connect_email(
    subject = "RStudio Connect HTML Email",
    attach_output = TRUE,
    attachments = c("mtp_KELLOGGS.csv", "mtp.csv")
  )
```

