---
title: "Email Document"
output: blastula::blastula_email
---

```{r packages, include=FALSE}
library(tidyverse)
```

# An R Markdown Document (Summary Report for Email)

We can include parts from the parent `"connect-example-main.Rmd"` document by adding an empty R Markdown code chunk with a matching name (in this case `mtp_plot`). This is great because we can reuse parts from the parent report document.

```{r mtp_plot, echo=FALSE}
```

The product table (from the parent document's `mtp_KELLOGGS` chunk) can be included in the same way:

```{r mtp_KELLOGGS, echo=FALSE}
```

Note that the `echo=FALSE` parameter was added to each of the the code chunks to prevent printing of the **R** code that generated the plot (we just want the output for the email).

The `mtp_KELLOGGS` object (from the namesake **R** code chunk) is also available and can be further processed to generate different output just for the email document.

```{r last_5_years, echo=FALSE}
mtp_KELLOGGS %>% filter(total_sales %in% 40000:50000)
```
